Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-17 writeup/gz_hubble_data.tex
Smaller changes (via email) from CJL.

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of color composite images. Images in GZH
were selected from various \textit{Hubble Space Telescope} Legacy programs
using the Advanced Camera for Surveys, with filters that probe the rest-frame
optical emission from galaxies out to $z\sim1$.  The bulk of the sample is
selected to have $m_{I814W}<23.5$ across AEGIS, COSMOS, GEMS, and 2-epoch
exposures in GOODS-N and GOODS-S. Full-depth 5-epoch images from the GOODS
fields are also included and have $m_{I814W}<26.8$. The median redshift of the
combined samples is $\langle z\rangle=0.9\pm0.6$, with a tail extending out to
$z\simeq4$. The GZH morphological data include measurements of both bulge- and
disk-dominated galaxies, details on spiral disk structure that relate to the
Hubble type, bar identification, and numerous measuremenst of clump
identification and geometry.  This paper also describes a new method for
calibrating morphological bias by using artificially-redshifted galaxy images
as a baseline. The GZH catalog contains both raw and calibrated morphological
vote fractions for $150,771$~galaxies, providing the largest dataset to date
suitable for large-scale studies of galaxy evolution out to $z\sim1$. 
\end{abstract}

@@

The morphology of galaxies encodes information on the orbital parameters and
assembly history of their contents, including gas, dust, stars, and the central
black hole. The morphology is also closely related to the local environment of
a galaxy, as interactions such as tides, shocks in cluster environments and
direct mergers can all influence a galaxy's internal structure.  For
$M^\star$~galaxies in the local Universe, this interplay between the physical
development of a galaxy and its external appearance typically manifests at the
most basic level as the difference between bulge-dominated systems with
no/little spiral structure (early-types) and disk-dominated,
rotationally-supported galaxies (late-types) frequently exhibiting spiral arms.
This dichotomy has been used to explore much of the astrophysics governing
galaxy formation and evolution, and has been shown to be closely linked with
other galactic properties such as stellar mass, halo mass, bolometric
luminosity, black hole activity, effective radius, and the relative ages of the
stellar populations.

The advent of larger telescopes in an increasing range of observing wavelengths
has revealed that the distribution and properties of galaxy morphology have
strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$
(roughly 6~Gyr after the Big Bang), many galaxies are still in the process of
assembling the baryonic and stellar mass required to reproduce the mature,
coherent structures seen at the present day. This growth occurs via a variety
of pathways, including accretion from large-scale galactic filaments onto halos
via streaming, mergers of individual halos, conversion of gas into stars via
gravitational collapse, etc. The accrual of baryons can be slowed or even
reversed via feedback from stellar winds, supernovae, and active black holes.
Each of these processes affects galaxy morphology in different ways, and so an
accurate measurement of morphological demographics as a function of redshift
provides an extremely powerful observational constraint on the physics involved
\citep[for recent reviews see][]{but13,con14}.

@@

Observational studies of galaxies at high-redshift also display a wide range of
morphological types, many of which are rare or absent at $z\sim0$. Although
spheroids and disks are present, they are typically much more compact than
those in the local Universe. There is also a significant population of more
irregular, massive galaxies, including mergers, tadpoles, chains,
double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}. In
contrast, while grand-design spirals have been observed as far back as $z=2.18$
\citep{law12}, their spatial density suggests that they are exceedingly rare,
with a very low fraction of undisturbed disks \citep{mor13}. Current
observational data thus strongly suggests that the classical Hubble
sequence/tuning fork \citep{hub36} is not a suitable framework for
characterizing high-redshift morphology.

Space-based observatories, particularly the \hubble{} (\hst), have been
responsible for the bulk of imaging studies of high-redshift galaxies.
Observations of fixed fields with very deep imaging
\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric
sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also
providing the angular resolution to distinguish internal structure and
characterize the morphology. While these measurements are helped by the fact
that the angular diameter distance is relatively flat beyond $z>1$ in a flat
$\Lambda$CDM cosmology, the relevant angular scales are only of the order
$\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve
much of the structure for a Milky Way-sized galaxy (at least for distinguishing
a disk from a bulge), but will be limited for more compact structures. Since
the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$
\citep{mao98,law12a}, the compact sizes of high-redshift galaxies make detailed
morphologies a challenge even for \hst{} \citep{che12}. The public availability
of more than $10^5$~galaxies in archival imaging across various studies gives a
data sample with the potential for high statistical significance.

@@

In the ACS-GC \citep{gri12}, individual galaxies were identified using a
combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
GOODS-S, and GOODS-N surveys, respectively. This yielded a total of
113,166~images (Table~\ref{tbl:gzh_numbers}).

@@

Stripe~82 single-epoch images were taken directly from the DR7 SDSS Skyserver,
which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
RGB channels. The co-added Stripe~82 images were assembled from runs 106 and
206 in DR7 and processed into color composites in a corresponding manner.

@@

GZH also included a set of images designed to measure the effect of active
galactic nuclei (AGN) on morphological classifications. Since galactic nuclei
can have bright, unresolved optical emission, AGN have the potential to mimic
or distort the identification of a bulge component. The presence of an AGN was
simulated by modeling the point spread function (PSF) of the telescope and then
inserting a bright source near the center of a real galaxy. For each image, the
simulated AGN was assigned one of three colors -- either blue, red, or flat
(white) as seen in the color images -- and a range of brightnesses such that
$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
with different simulated AGN for each host.

Two sets of simulated AGN were generated in GZH. The first set (version~1) was
assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by combining stars in the GOODS fields using the PSF creation tools in \texttt{daophot}. 
The second set (version~2) was assembled from 96~galaxies in GOODS-S; this
version used simulated PSFs from \texttt{TinyTim} \citep{kri93}, drizzled using the same procedures as those used in reduction of the GOODS-S images \citep{koe02,koe03,gia04}. The use of these 2 versions facilitates comparisons between these different PSF creation methods, which are widely used in AGN host galaxy morphology studies \citep[e.g.,][]{san04,sim08,pie10a,simm11}. 
% okay so I'm a cheeky self-citing biyotch
Each PSF creation method has advantages and disadvantages: the empirical PSFs better represent the nuances of the PSF in the specific data being used and look more realistic at lower luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs are visually more realistic at higher luminosities.

@@

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. The first
priority is spectroscopic redshifts; these were taken from the ACS-GC
\citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A
high-quality spectroscopic redshift in the ACS-GC is the primary option; if
none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in
3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more
than 98\% are consistent ($\Delta z<0.001$), and so the order of selection
made no practical difference. Galaxies with inconsistent spectroscopic
redshifts between any pair of catalogs are marked with a flag in
Table~\ref{tbl:catalog_hst}. If no spectroscopic redshifts were available, the
1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC,
UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
redshift with the smallest error. 
%Table~\ref{tbl:redshifts} shows the results of this selection.

@@

The GZH decision tree had four broad sets of morphologies. The first option
designated stars or image artifacts (the result of either bad data or incorrect
classification by the ACS pipeline as a galaxy); in this case, the
classification process ended and no further questions were asked. The second
set were smooth galaxies, intended to select ellipticals/early-types;
classifiers also measured the relative axial ratio (roundness) for these
galaxies. The third set was for disk/late-type galaxies, which measured the
features necessary to place a galaxy on the standard Hubble tuning fork (bars,
spiral arm, strength of the central bulge). The final set, which was new in
this phase of Galaxy~Zoo and designed for high-redshift targets, identified
objects dominated by clumpy morphologies. Further annotations for clumpy
galaxies included assessing the number, arrangement, relative brightness, and
location of the clumps within the galaxy. Finally, every classification of a
galaxy gave the option of identifying ``odd'' features within the image; these
labels were for relatively rare $(\lesssim1\%)$ phenomena, including dust
lanes, gravitational lenses, and mergers.

@@

As a first step to producing consensus classifications of each galaxy, 
the votes of individual classifiers in GZH were combined to make a vote
fraction for each response ($f_{response}$) to a question in the classification
tree. Votes were subsequently weighted and re-combined in an iterative method similar that in 
previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a method chosen 
to be as egalitarian as possible while also identifying and downweighting classifiers 
who frequently disagreed with others. The weighting factor $(w)$ was 1 for the
top 95\% of classifiers, as ranked by consistency. For the bottom 5\% of
classifiers, $w$ was designed to drop smoothly and was effectively zero for the
bottom 1\%.  Since this only affected a tiny percentage of the classifiers (and
% would be good to quantify "tiny" and "even smaller [than tiny]"
an even smaller percentage of the classifications) the overall effect on the
GZH dataset was minimal. The method was effective, however, at filtering out
contributions from random or deliberately malicious classifiers.

@@

The previous versions of Galaxy Zoo morphology classifications
\citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital
Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it
was assumed that there was no cosmological evolution of the morphologies of
galaxies and therefore any observed changes in the distribution of galaxies
with different consensus morphologies was due to the effects of redshift on the
image quality (\ie, the reduction in physical resolution, surface brightness
dimming, etc). For both previous releases of GZ morphologies, a correction for
redshift-dependent bias was applied based on matching the classification
fractions at the highest redshifts with those at the lowest redshift.
\citet{bam09} and \citet{wil13} provide complete descriptions of the process
for GZ1 and GZ2, respectively.

@@

The approach used in GZH for correcting the weighted classifications for redshift
bias rests on the assumption that the \emph{amount} of bias is a function of
the apparent size and brightness of the image as seen on screen. This is
controlled by two types of parameters: \textbf{intrinsic} properties of the
galaxy itself, such as its physical diameter and luminosity, and
\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
and its relative orientation. There may also be other parameters that affect
classifier accuracy, such as the proximity of close companions \citep[``distraction
bias''; see][]{joh15} or bias as a function of individual classifier ability and
skill. The combination of all such parameters forms a high-dimensional space,
and it is not clear how to separate this into individual effects. Instead, the
method used here employs only two parameters intended to capture the bulk of
the change in bias: the $r^\prime$-band surface brightness ($\mu_r$; intrinsic)
and redshift ($z$; extrinsic).

The change in bias as a function of $\mu_r$ and \zsim{} is measured using the
\ferengi{} images over all the evolutionary correction factors. It is assumed
that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be
expressed as:

@@

As with the HST images, each \ferengi{} subject had a varying number of classifiers
answering the various questions in the hierarchical decision tree. Every classifier
answers the first question, {\it ``Is the galaxy smooth and rounded, with no
sign of a disk?''}; as such the vote fractions \fsmooth, \ffeatures, and
\fartifact{} are all computed with the minimum statistical error for any
question, with between 40 and 140~responses (see Section~\ref{sec:interface}).
The number of participants answering subsequent questions, however, is always equal
to or less than the number who answered the preceding question. The average number
of responses per task for fourth- or fifth-tier questions such as spiral arm
structure (Tasks 12--14) is only $4\pm4$ for the \ferengi{} sample; while this
is distribution is strongly bimodal (reflecting the true morphologies of
selected galaxies), the very low absolute numbers of votes introduce very high
variance when attempting to calculate a statistical correction.

@@

The intended purpose of the GZH catalog is to provide a simple, yet flexible,
means of identifying samples of galaxies with a desired morphological type.
This section provides instructions for creating such samples using the vote
fractions corresponding to the tasks shown in Figure~\ref{fig:decisiontree}. We
stress that the selection process will vary based on the particular science
case. More conservative cuts can be applied to create pure, but not necessarily
complete, samples. These are useful for selecting galaxies exhibiting unique
morphologies for individual case studies or observing proposals. Looser cuts
can be applied to obtain samples with a higher level of completeness, which
will increase the sample size but can potentially decrease purity. Population
studies would make use of such large samples, in which statistical significance
is a crucial factor in evaluating results. \citet{mas11c,mel14,che15}, and
\citet{gal15} are examples of GZ papers which select morphologies in this way.

@@

All of the Legacy surveys included in the GZH imaging have had morphological
catalogs previously published; these catalogs have significant differences in
the number of galaxies, size and magnitude limits, classification scheme, and
the methods used for measuring morphology. These catalogs have been
cross-matched to GZH to compare the results; this is not presented as an
endorsement of any particular method, but as an exploration of the strengths
and weaknesses of the GZ crowdsourced catalogs as compared to products made
with machine learning, automatic fits, and expert visual classification.

@@

KS gratefully acknowledges support from Swiss National Science Foundation Grant
PP00P2\_138979/1.

@@

GZH used both 5-epoch and 2-epoch sets of data to construct the GOODS set of
images. The 11,157 full depth 5-epoch images are used in the main catalog; the
classifications for the 7,464 shallow depth 2-epoch images are provided as a
supplementary table. This section analyzes the effect of image depth on the
ability of the GZ classifiers to identify features or disk structure in the images.

>>>>

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of color composite images. Images in GZH
were selected from various \textit{Hubble Space Telescope} Legacy programs
using the Advanced Camera for Surveys, with filters that probe the rest-frame
optical emission from galaxies out to $z\sim1$.  The bulk of the sample is
selected to have $m_{I814W}<23.5$ across AEGIS, COSMOS, GEMS, and 2-epoch
exposures in GOODS-N and GOODS-S. Full-depth 5-epoch images from the GOODS
fields are also included and have $m_{I814W}<26.8$. The median redshift of the
combined samples is $\langle z\rangle=0.9\pm0.6$, with a tail extending out to
$z\simeq4$. The GZH morphological data include measurements of both bulge- and
disk-dominated galaxies, details on spiral disk structure that relate to the
Hubble type, bar identification, and numerous measuremenst of clump
identification and geometry.  This paper also describes a new method for
calibrating morphologies for galaxies of different luminosities and at
different redshifts by using artificially-redshifted galaxy images as a
baseline. The GZH catalog contains both raw and calibrated morphological vote
fractions for $150,771$~galaxies, providing the largest dataset to date
suitable for large-scale studies of galaxy evolution out to $z\sim1$. 
\end{abstract}

@@

The morphology of galaxies encodes information on the orbital parameters and
assembly history of their contents, including gas, dust, stars, and the central
black hole. The morphology is also closely related to the local environment of
the galaxy, as mutual interactions such as tides, shocks in cluster
environments, and direct mergers can all change the shape of the galaxy's
gravitational potential. For $M^\star$~galaxies in the local Universe, this
interplay between the physical development of a galaxy and its external
appearance typically manifests at the most basic level as the difference
between bulge-dominated systems with no/little spiral structure (early-types)
and disk-dominated, rotationally-supported galaxies (late-types) frequently
exhibiting spiral arms.  This dichotomy has been used to explore much of the
astrophysics governing galaxy formation and evolution, and has been shown to be
closely linked with other galactic properties such as stellar mass, halo mass,
bolometric luminosity, black hole activity, effective radius, and the relative
ages of the stellar populations.

The advent of larger telescopes in an increasing range of observing wavelengths
has revealed that the distribution and properties of galaxy morphology have
strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$
(roughly 6~Gyr after the Big Bang), many galaxies are still in the process of
assembling the baryonic mass required to reproduce the mature, coherent
structures seen in the present day. This growth occurs in a variety of
pathways, including accretion of baryons from large-scale galactic filaments
onto halos via streaming, mergers of individual dark matter halos along with
their baryons, conversion of gas into stars through gravitational collapse and
star formation, etc. The process can also be slowed or even reversed via
feedback from stellar winds, supernovae, and active black holes.  Each of these
processes affects the galaxy morphology in different ways, and so an accurate
measurement of the demographics as a function of redshift provides an extremely
powerful observational constraint on the physics involved \citep[for recent
reviews see][]{but13,con14}.

@@

Observational studies of galaxies at high-redshift also display a wide range of
morphological types, many of which are rare or absent at $z\sim0$.  These
include spheroids and disks (akin to the ellipticals and spirals seen in the
local Universe), but also a significant population of massive, more irregular
galaxies, including mergers, tadpoles, chains, double-clumps, and
clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}.  In contrast, while
grand-design spirals have been observed as far back as $z=2.18$ \citep{law12},
their spatial density suggests that they are exceedingly rare at these high
redshifts, with a very low overall disk fraction \citep{mor13}. Current
observational data thus strongly suggests that the classical Hubble
sequence/tuning fork \citep{hub36} is not a suitable framework for
characterizing high-redshift morphology.

Space-based observatories, particularly the \hubble{} (\hst), have been
responsible for the bulk of imaging studies of high-redshift galaxies.
Observations of fixed fields with very deep imaging
\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric
sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also
providing the angular resolution to distinguish internal structure and
characterize the morphology. While these measurements are helped by the fact
that the angular diameter distance is relatively flat beyond $z>1$ in a flat
$\Lambda$CDM cosmology, the relevant angular scales are only of the order
$\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve
much of the structure for a Milky Way-sized galaxy out to moderately high
redshifts (at least distinguishing a disk from a bulge), but is limited for
more compact structures. Since the size of galaxies evolves as roughly
$r\propto(1+z)^{-1}$ \citep{mao98,law12a}, the compact sizes of high-redshift
galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}.
The public availability of more than $10^5$~galaxies in archival imaging across
various studies gives a data sample with the potential for high statistical
significance.

@@

In the ACS-GC \citep{gri12}, individual galaxies were identified using a
combination of \sextractor{} \citep{ber96} and the \sersic-profile fitting
framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
GOODS-S, and GOODS-N surveys, respectively. This yielded a total of
113,166~images (Table~\ref{tbl:gzh_numbers}).

@@

Stripe~82 single-epoch images were taken directly from the DR7 SDSS Skyserver,
which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
RGB channels. The co-added Stripe~82 images were assembled from runs 106 and
206 in DR7 and processed into color composites in the same manner as previous
iterations of Galaxy~Zoo.

@@

GZH also included a set of images designed to measure the effect of active
galactic nuclei (AGN) on morphological classifications. Since galactic nuclei
can have bright, unresolved optical emission, AGN have the potential to mimic
or distort the identification of a bulge component. The presence of an AGN was
simulated by modeling the point spread function (PSF) of the telescope and then
inserting a bright source near the center of a real galaxy. For each image, the
simulated AGN was assigned one of three colors -- either blue, red, or flat
(white) as seen in the color images -- and a range of brightnesses such that
$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
$(0.2,1.0,2.0,5.0,10.0,50.0)$. This range was selected to run from AGN which
were all but undetectable through to those which dominate the galaxy, providing
coverage of all plausible effects. Combining these parameters generated
15~images with different simulated AGN for each host.

Two sets of simulated AGN were generated in GZH. The first set (version~1) was
assembled from 95~galaxies from GOODS-S imaging and empirical PSFs made by
combining stars in the GOODS fields using the PSF creation tools in
\texttt{daophot}.  The second set (version~2) was assembled from 96~galaxies in
GOODS-S; this version used simulated PSFs from \texttt{TinyTim} \citep{kri93},
drizzled using the same procedures as those used in reduction of the GOODS-S
images \citep{koe02,koe03,gia04}. The use of these 2 versions facilitates
comparisons between these different PSF creation methods, which are widely used
in AGN host galaxy morphology studies
\citep[e.g.,][]{san04,sim08,pie10a,simm11}.  Each PSF creation method has
advantages and disadvantages: the empirical PSFs better represent the nuances
of the PSF in the specific data being used and look more realistic at lower
luminosities, but the extended features of the noiseless \texttt{TinyTim} PSFs
are visually more realistic at higher luminosities.
% okay so I'm a cheeky self-citing biyotch

@@

For galaxies which have published redshifts from multiple sources, the
following algorithm was used to select the $\tt Z\_BEST$ quantity. A
high-quality spectroscopic redshift in the ACS-GC is the primary option,
provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC
\citep{car10} catalogs and used in that order. For galaxies with multiple
spectroscopic redshifts, more than 98\% are consistent ($\Delta z<0.001$), and
so the order of selection made no practical difference. Galaxies with
inconsistent spectroscopic redshifts between any pair of catalogs are marked
with a flag in Table~\ref{tbl:catalog_hst}. If no spectroscopic redshifts were
available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST,
MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data were used to select the
estimated redshift with the smallest error. 
%Table~\ref{tbl:redshifts} shows the results of this selection.

@@

The GZH decision tree was designed to remain close to that used by GZ2 while
taking account of the likely differences in high redshift systems, and has four
broad sets of morphologies classified by the users.  The first option
designated stars or image artifacts (the result of either bad data or incorrect
identification as a galaxy by the ACS pipeline); in this case, the
classification process ended and no further questions were asked. The second
set was smooth galaxies, intended to select ellipticals/early-types;
volunteers also indicate the relative axial ratio (roundness) for these
galaxies. The third set was for disk/late-type galaxies, which measured the
features necessary to place a galaxy on the standard Hubble tuning fork (bars,
spiral arm, strength of the central bulge). The final set, which was new in
this phase of Galaxy~Zoo and designed for high-redshift targets, identified
objects dominated by clumpy morphologies. Further annotations for clumpy
galaxies included assessing the number, arrangement, relative brightness, and
location of the clumps within the galaxy. Finally, every classification of a
galaxy gave the option of identifying ``odd'' features within the image; these
labels were for relatively rare $(\lesssim1\%)$ phenomena, including dust
lanes, gravitational lenses, and mergers.

@@

As a first step to producing a consensus measurement of each galaxy, the votes
of individual volunteers who classified galaxies in GZH were combined to make a
vote fraction for each response ($f_{response}$) to a question in the decision
tree. Votes were subsequently weighted and re-combined in an iterative method
similar that in previous versions of Galaxy~Zoo \citep{lan08,wil13}, using a
method chosen to be as egalitarian as possible while also identifying and
downweighting classifiers who frequently disagreed with others. The weighting
factor $(w)$ was 1 for the top 95\% of classifiers, as ranked by consistency.
For the bottom 5\% of classifiers, $w$ was designed to drop smoothly and was
effectively zero for the bottom 1\% in the distribution function. Since this
only affected a tiny percentage of the classifiers (and an even smaller
percentage of the classifications) the overall effect on the GZH dataset was
minimal. The method was effective, however, at filtering out contributions from
randomly classifying or malicious participants.
% would be good to quantify "tiny" and "even smaller [than tiny]"

@@

The previous versions of Galaxy Zoo morphology classifications
\citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital
Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it
was assumed that there was no cosmological evolution of the morphologies of
galaxies and therefore any observed changes in the distribution of galaxies
with different consensus morphologies was due to the effects of redshift on the
image quality (\ie, the reduction in physical resolution, surface brightness
dimming, etc). For both previous releases of Galaxy~Zoo morphologies, a correction for
redshift-dependent bias was applied based on matching the classification
fractions at the highest redshifts with those at the lowest redshift.
\citet{bam09} and \citet{wil13} provide complete descriptions of the process
for GZ1 and GZ2, respectively.

@@

The approach used in GZH for correcting the weighted classifications for redshift
bias rests on the assumption that the \emph{degree} of bias is a function of
the apparent size and brightness of the image as seen on screen. This is
controlled by two types of parameters: \textbf{intrinsic} properties of the
galaxy itself, such as its physical diameter and luminosity, and
\textbf{extrinsic} properties, such as the distance (redshift) of the galaxy
and its relative orientation. There may also be other parameters that affect
classifier accuracy, such as the proximity of close companions \citep[``distraction
bias''; see][]{joh15} or bias as a function of individual classifier ability and
skill. The combination of all such parameters forms a high-dimensional space,
and it is not clear how to separate this into individual effects. Instead, the
method used here employs only two parameters intended to capture the bulk of
the change in bias: the $r^\prime$-band surface brightness ($\mu_r$; intrinsic)
and redshift ($z$; extrinsic).

The change in bias as a function of $\mu_r$ and \zsim{} is measured using the
\ferengi{} images over all the evolutionary correction factors. It is assumed
that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for an
artificially-redshifted galaxy can be expressed as:

@@

As with the HST images, each \ferengi{} subject had a varying number of classifiers
answering the various questions in the hierarchical decision tree. Every classifier
answers the first question, {\it ``Is the galaxy smooth and rounded, with no
sign of a disk?''}; as such the vote fractions \fsmooth, \ffeatures, and
\fartifact{} are all computed with the minimum statistical error for any
question, with between 40 and 140~responses (see Section~\ref{sec:interface}).
The number of participants answering subsequent questions, however, is always equal
to or less than the number who answered the preceding question. The average number
of responses per task for fourth- or fifth-tier questions such as spiral arm
structure (Tasks 12--14) is only $4\pm4$ for the \ferengi{} sample; while this
distribution is strongly bimodal (reflecting the true morphologies of
selected galaxies), the very low absolute numbers of votes introduce very high
variance when attempting to calculate a statistical correction.

@@

The intended purpose of the GZH catalog is to provide a simple, yet flexible,
means of identifying samples of galaxies with a desired morphological type.
This section provides instructions for creating such samples using the vote
fractions corresponding to the tasks shown in Figure~\ref{fig:decisiontree}. We
stress that the selection process will vary based on the particular science
case. More conservative cuts can be applied to create pure, but not necessarily
complete, samples. These are useful for selecting galaxies exhibiting unique
morphologies for individual case studies or observing proposals. Looser cuts
can be applied to obtain samples with a higher level of completeness, which
will increase the sample size but can potentially decrease purity. Population
studies would make use of such large samples, in which statistical significance
is a crucial factor in evaluating results. \citet{mas11c,mel14,che15}, and
\citet{gal15} are examples of Galaxy~Zoo papers which select morphologies in this way.

@@

All of the Legacy surveys included in the GZH imaging have had morphological
catalogs previously published; these catalogs have significant differences in
the number of galaxies, size and magnitude limits, classification scheme, and
the methods used for measuring morphology. These catalogs have been
cross-matched to GZH to compare the results; this is not presented as an
endorsement of any particular method, but as an exploration of the strengths
and weaknesses of the Galaxy~Zoo crowdsourced catalogs as compared to products made
with machine learning, automatic fits, and expert visual classification.

@@

The development and hosting of Galaxy Zoo Hubble was supported by a grant from
the Alfred P. Sloan Foundation. The Zooniverse acknowledges support from a
Google Global Impact Award. KS gratefully acknowledges support from Swiss
National Science Foundation Grant PP00P2\_138979/1.

@@

GZH used both 5-epoch and 2-epoch sets of data to construct the GOODS set of
images. The 11,157 full depth 5-epoch images are used in the main catalog; the
classifications for the 7,464 shallow depth 2-epoch images are provided as a
supplementary table. This section analyzes the effect of image depth on the
ability of the Galaxy~Zoo classifiers to identify features or disk structure in the images.
